On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-05 Manuscript/reply.tex
comments on the reply

@@

Below is an example of what this would look like. We find that it is a little
cluttered to make comparisons, so we will use the original format.

@@

@@

Because of the style constraints for AJUR, we have removed page numbers in 
citations.

@@

\eds{I don't think this answers the question.  The reviewer is saying that 0.95 
is close to the boundary of 1, so the undercoverage observed intervals
(especially when phi -0.4) may be due, at least in part, to the flaws 
of the asymptotic Wald interval you are using. 
\@ Jun: do you think he should try exact Clopper-Pearson
intervals for at least a few cases of undercoverage to verify it is not the Wald
interval that is causing the undercoverage, then comment on this in at least the
reply (and possibly also in the main paper)?}
\mc{plot\_norm\_mu\_1\_cup.pdf (exact Clopper-Pearson) seems to have about the same 
widths for high 
proportions
(especially for phi = -0.4) as {plot\_norm\_mu\_1.pdf} (Wald-Type)}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1_cp}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs 
    for
    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
    error bars represent 95\% exact CIs of the real coverage rates.}
  \label{fig:norm_mu_1_cp}
\end{figure}

@@

\eds{\@ Jun: what do you think about putting the $l = \lceil 2n^{1/3} \rceil$
results in the Appendix, but keeping the conclusions regarding how the 
$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$ simulations differ
in the main text?}
\mc{I moved everything to the Appendix. if you want to change it back you can 
revert the commit}

>>>>

\jy{For each comment, response first and at the end of each response,
  state what was done in the text. I usually don't quote text because
  if you make changes, you need to synchronize at two locations. Learn
  from the first version (which is a real reply letter for a paper).}

@@

\jy{never use ``below'' because tables/figures are floats.}

Figure~\ref{fig:mu} is an example of what this would look like. We find that it is a little
cluttered to make comparisons, so we will use the original format.

\jy{1. Reduce the heights; put legend at the bottom; put the
  confidence intervals side by side for each sample size (see this
  paper for example plot:
  \url{https://iopscience.iop.org/article/10.1088/1748-9326/ac14ee/meta}.}

@@

\jy{Left quote: `` (below the ESC key)}

@@

Because of the bib style constraints for AJUR, we have removed page numbers in 
citations.

@@

\eds{I don't think this answers the question.  The reviewer is saying that 0.95 
is close to the boundary of 1, so the undercoverage observed intervals
(especially when phi -0.4) may be due, at least in part, to the flaws 
of the asymptotic Wald interval you are using. 
\@ Jun: do you think he should try exact Clopper-Pearson
intervals for at least a few cases of undercoverage to verify it is not the Wald
interval that is causing the undercoverage, then comment on this in at least the
reply (and possibly also in the main paper)?}
\mc{plot\_norm\_mu\_1\_cup.pdf (exact Clopper-Pearson) seems to have about the same 
widths for high 
proportions
(especially for phi = -0.4) as {plot\_norm\_mu\_1.pdf} (Wald-Type)}
\jy{I thought the CP interval is for binomial proportions. How was it
  done here?}

@@

\jy{No  need to duplicate the figures if they are already in the paper.}
\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1_cp}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs 
    for
    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
    error bars represent 95\% exact CIs of the real coverage rates.}
  \label{fig:norm_mu_1_cp}
\end{figure}

@@

\eds{\@ Jun: what do you think about putting the $l = \lceil 2n^{1/3} \rceil$
results in the Appendix, but keeping the conclusions regarding how the 
$l = \lceil n^{1/3} \rceil$ and $l = \lceil 2n^{1/3} \rceil$ simulations differ
in the main text?} \jy{I agree. Mention the results in the text and
refer to the appendix.}
\mc{I moved everything to the Appendix. if you want to change it back you can 
revert the commit}
